Meeting --- Summary LLM

### 2024-03-14 meetings/18-01-2024_slides.qmd
typos

---
title: "Meeting --- Summary LLM"
author: "Bas Doners, Dennis Fok, Finn-Ole Höner"
date: 2024-01-18
date-format: long
format: beamer
aspectratio: 169
incremental: false
include-in-header: ../beamer_preamble.tex
bibliography: ../references.bib
fig-align: center
fig-cap-location: bottom
fig-format: pdf
links-as-notes: true
number-depth: 1
---

>>>>

---
title: "Meeting --- Summary LLM"
author: "Bas Donkers, Dennis Fok, Finn-Ole Höner"
date: 2024-01-18
date-format: long
format: beamer
aspectratio: 169
incremental: false
include-in-header: ../beamer_preamble.tex
bibliography: ../references.bib
fig-align: center
fig-cap-location: bottom
fig-format: pdf
links-as-notes: true
number-depth: 1
---
